---
output:
  html_document:
    keep_md: yes
---
The Code Book
======================================

It describes the variables, the data, and any transformations or work that I performed to clean up the data used by the R code `run_analysis.R`. 

## Raw data
Form the weblink 

[https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip)

we download a folder named `UCI HAR Dataset`.

In the README file of this folder there is an explanation for the data source.
The experiments was carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person had performed six activities wearing a smartphone (Samsung Galaxy S II) on the waist.

Using its embedded accelerometer and gyroscope, they captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments was video-recorded to label the data manually. Then, the obtained dataset was randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. 

### Activity
The activities are label as follows:

- 1 WALKING
- 2 WALKING_UPSTAIRS
- 3 WALKING_DOWNSTAIRS
- 4 SITTING
- 5 STANDING
- 6 LAYING 

### Features
The list of features is cointained in the file `features.txt`:
```{r read_features}
features <- read.table("UCI HAR Dataset/features.txt", col.names = c("id","name")) # read features names
dim(features)
head(features)
tail(features,20)
```
where `t` at the beginning of the variable names stands for `time` and `f` for `frequency`.

The set of variables that were estimated from these signals are:

- mean(): Mean value
- std(): Standard deviation
- mad(): Median absolute deviation 
- max(): Largest value in array
- min(): Smallest value in array
- sma(): Signal magnitude area
- energy(): Energy measure. Sum of the squares divided by the number of values. 
- iqr(): Interquartile range 
- entropy(): Signal entropy
- arCoeff(): Autorregresion coefficients with Burg order equal to 4
- correlation(): correlation coefficient between two signals
- maxInds(): index of the frequency component with largest magnitude
- meanFreq(): Weighted average of the frequency components to obtain a mean frequency
- skewness(): skewness of the frequency domain signal 
- kurtosis(): kurtosis of the frequency domain signal 
- bandsEnergy(): Energy of a frequency interval within the 64 bins of the FFT of each window.
- angle(): Angle between to vectors.

All the information about the variables used on the feature vector are provided in the file `features_info.txt`of the downloaded folder.

### Measurements
The measurements, the ativity labels and the identifier of the subject who carried out the experiment are contained in different files.

In `UCI HAR Dataset/train` folder we find information for the training data:
- `X_train.txt` containts the measurements.
- `y_train.txt` containts the ativity labels (from 1 to 6).
- `subject_train.txt` contains the subject identifier (from 1 to 30).

In `UCI HAR Dataset/test` folder we find information for the test data:
- `X_test.txt` containts the measurements.
- `y_test.txt` containts the ativity labels (from 1 to 6).
- `subject_test.txt` contains the subject identifier (from 1 to 30).

The traing and test dataset can be read for axample using R by:
```{r read_data,cache=TRUE}
x_train <- read.table("UCI HAR Dataset/train/X_train.txt") # read training data
dim(x_train)
x_test <- read.table("UCI HAR Dataset/test/X_test.txt")    # read test data
dim(x_test)
```
and we notice that the number of columns of the each dataset is `r ncol(x_test)`. So, for each features, the row number correspond to the column number in the measurement dataset.

## Processing data
No process has been made for this analysis.

